When the robot considers the human...

### 2013-04-23 paper.tex
Complete biblio

Spatial reasoning~\cite{OKeefe1999}, on the other hand, has been used
for natural language processing for applications such as direction
recognition ~\cite{Kollar10,Matuszek10} or language
grounding~\cite{Tellex10}.~\cite{Skubic2004} presented a spatial
reasoner integrated in a robot which computes symbolic positions of
objects.

\begin{figure}[htb]
\centering
\includegraphics[width=9cm]{figs/grounding_robot.pdf}
\caption{Robot reasoning about HRI and anticipation of human activities:
  sources of information are multi-modal dialogue, and observation of
  environment and human activity}
\label{fig:hri-dec}
\end{figure}

>>>>

Spatial reasoning~\cite{O'Keefe1999}, on the other hand, has been used
for natural language processing for applications such as direction
recognition ~\cite{Kollar2010,Matuszek2010} or language
grounding~\cite{Tellex2010}.~\cite{Skubic2004} presented a spatial
reasoner integrated in a robot which computes symbolic positions of
objects.

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\columnwidth]{figs/grounding_robot.pdf}
\caption{Robot reasoning about HRI and anticipation of human activities:
  sources of information are multi-modal dialogue, and observation of
  environment and human activity}
\label{fig:hri-dec}
\end{figure}
